Exploratory overview of Berlin city trees

### 2020-01-13 analysis/paper/paper.Rmd
cont work

```{r fig-tree-overview-map, fig.cap="A plot of random numbers",fig.width = 15, fig.height = 8, out.width="100%"}
readd(plot_overview_map)
# plot_overview_map

>>>>

```{r fig-bar-tree, fig.cap="A plot of random numbers",fig.width = 15, fig.height = 8, out.width="100%"}

# loadd(full_data_set_clean)
# loadd(plot_overview_map)
# print(class(full_data_set_clean))
readd(plot_tree_sums_bar)
# plot_overview_map

```{r fig-tree-overview-map, fig.cap="A plot of random numbers",fig.width = 15, fig.height = 8, out.width="100%"}

# loadd(full_data_set_clean)
# loadd(plot_overview_map)
# print(class(full_data_set_clean))
readd(plot_overview_map)
# plot_overview_map
